Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-01 paper/paper.tex
abstract v1

This model is evaluated in a retrieval task using a perceptually defined retrieval objective. Computational experiments demonstrates 1) the importance of handling long term modulations both in time and frequency, with a gain of $14\%$ in precision compared to Mfccs  2) the relevance of a learned layer that is able provide an average gain of $3\%$ in precision with a halving of the variance.

>>>>

This model is evaluated in a retrieval task using a perceptually defined retrieval objective. Computational experiments demonstrates 1) the importance of handling long term modulations both in time and frequency, with a gain of $14\%$ in precision compared to Mfccs  2) the relevance of a learned layer that is able provide an average gain of $3\%$ in precision with a reduction of the variance of the prediction error of a factor of 2.
